---
title: "W_UP_01"
author: "Diana Flores"
date: "Summer 2023 "
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

We are trying to find the average number of push up between skill players and line players. Is there a statistical difference in the average number of push ups between both positions.


Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

I will be using the Num~Cat numerical for the number average of push and categorical for the different positions.The method i will use will be a box plot we will also be a numerical summery for a numerical descriptive results . Lastly we will include a t-test.


<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

```{r}
boxplot(pushups~position,data=mydata)
```

The box plot shows that skills payers on average do about 60 pushups and the line positions does less than 20 on average.This study was done in a two minute time frame.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```

We have found the mean to be 17 for line players and 50 f0r skill players. The difference in means is 33 push-ups.

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```


The t test show that there is a difference in average push-ups for line players and skill players the difference is 33 push ups more than line players. 95 percent of the time the skills players do between 20-45 more push ups in two mins than a line player.The p value .000009421 this is so small number which leads us to  we reject the null hypothesis 


# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->



The original question what is who does more push ups on average skill players or line players. Is there a statistical difference? We have found there is a difference on push ups done per line skills players. The difference is 95 percent of the players do 20 to 45 push ups  more than a liner player.The p vlaue leads us to reject the null hypothesis.We have found their is a statistical difference. 
